\documentclass[../main.tex]{subfiles}

\begin{document}
\section{Conclusion}

\subsection{Summary of Findings}
\noindent
On the PathMNIST test set the convolutional neural network achieved the
strongest overall performance, reaching
76.76\% accuracy and
75.63\% macro-$F_{1}$. The
\gls{PCA}-reduced \gls{RBF} \gls{SVM} remained competitive
(69.01\% accuracy,
68.26\% macro-$F_{1}$), while the multilayer perceptron performed
substantially worse
(56.90\% / 53.50\%). These results strongly support the theoretical
importance of spatial inductive biases for histopathology image
classification. The \gls{MLP} treats each pixel independently and
therefore struggles to capture the local texture patterns and spatial
relationships that distinguish tissue types. Although the \gls{SVM}
benefits from a flexible non-linear decision boundary after dimensionality
reduction, it still operates on flattened image vectors and therefore
cannot fully exploit spatial structure.

\noindent
The \gls{CNN} clearly benefits from convolutional feature extraction,
which directly models local texture and translation-aware patterns. Even
the relatively small two-block architecture used in this assignment is
able to learn substantially more effective representations than either
the kernel-based or fully connected alternatives. The results therefore
demonstrate that convolutional inductive biases remain highly effective
even on low-resolution medical-image datasets such as PathMNIST.

\noindent
Runtime analysis revealed a trade-off between predictive performance and
computational efficiency. The \gls{SVM} trained quickly
($10.7\,\text{s}$) but suffered from slow inference
($7.0\,\text{s}$ for
8{,}000 test images) because predictions require comparisons against the
support vectors. The \gls{MLP} achieved the fastest inference time
($0.16\,\text{s}$) but delivered substantially weaker classification
performance. Although the \gls{CNN} required the longest training time
($65.0\,\text{s}$), it maintained practical inference speed
($0.60\,\text{s}$) while achieving the best predictive performance,
making it the most balanced choice overall for this dataset.

\subsection{Limitations}
\noindent
Several caveats should temper these conclusions. First, the search grids
were deliberately small to fit the available compute; broader grids over
network depth, weight decay and learning-rate schedules could change the
relative ranking, especially between the \gls{MLP} and the \gls{CNN}.
Second, the SVM was tuned on a stratified 5{,}000-sample subset to keep
the kernel computation tractable; the full-data refit improves accuracy
modestly but might benefit further from a re-tuned grid at the larger
scale, particularly for the kernel bandwidth $\gamma$. Third, we did not
apply data augmentation; on a larger study the marginal benefit of
augmentation versus the increased training-time budget should be measured
explicitly. Finally, the PathMNIST 28$\times$28 resolution is much
coarser than the source slides — extrapolating these conclusions to
clinical-resolution images would require re-running the comparison on a
higher-resolution variant such as PathMNIST-224.

\subsection{Future Work}
\noindent
Three concrete directions would strengthen the study. (i) Replace the
exhaustive grid for the neural networks with a random or Bayesian
hyper-parameter search over a larger space (depth, weight decay,
optimiser, and learning-rate schedule) to test whether the present
\gls{CNN} lies near the Pareto frontier of predictive performance versus
computational cost~\cite{bergstra2012random}. (ii) Re-evaluate the
comparison on PathMNIST-224, where convolutional inductive biases should
matter more strongly and where the \gls{SVM} would likely require either
a stronger feature extractor (e.g.~\gls{PCA} applied to features from a
pre-trained backbone) or replacement by a simpler linear baseline,
providing a clearer picture of the scaling behaviour of the different
model families. (iii) Calibrate per-class predictions and report
uncertainty metrics such as expected calibration error, since clinical
deployment of any of these models would require reliable confidence
estimates and the three classifier families differ substantially in how
their probability outputs behave.

\end{document}
